Reading Notes

### 2020-08-04 1summ.tex
writing for today. good progress on summary c:

\begin{center}
\large{\textbf{<Title>}}
%\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
\end{center}
\begin{center}
    Jenny W. Fothergill
\end{center}
\begin{center}
    \textbf{Project Summary}
\end{center}

%\begin{center}
%\emph{Maximum of 1 page}
%\end{center}
% This should be a brief statement of the problem you plan to address.
% It should look something like an abstract.

@@

@@

@@

>>>>

\begin{center}
\large{\textbf{<Title>}}
%\large{\textbf{ADVANCEMENT OF ORGANIC PHOTOVOLTAICS THROUGH ARTIFICIAL NEURAL NETWORKS}}
\end{center}
\begin{center}
    Jenny W. Fothergill
\end{center}
\begin{center}
    \textbf{Project Summary}
\end{center}
%\begin{center}
%\emph{Maximum of 1 page}
%\end{center}
% This should be a brief statement of the problem you plan to address.
% It should look something like an abstract.

@@

Already the effects of human-influenced climate change are <hurtng everyone in particular poor and disadvantaged groups>.
Burning fossil fuels for energy contributes to rising $CO_{2}$ levels.
And the energy demand is only increasing.
This makes finding efficient, renewable energy technologies of the utmost importance.
Harvesting solar energy is one way to help this problem.
Organic photovoltaic (OPV) devices have recieved attention for their simple, inexpensive manufacture.
Generally OPV devices are made of a multicompound mixture: usually an electron donor and acceptor which form a mosaic-like structure called a bulk-heterojunction (BHJ).
The compounds and polymers used in OPVs are made of common elements and can be synthesized with relative ease.
<opvs work by... sunlight excites an electron, forms an exciton, exciton travels to an interface, is dissociated, then the free charge travels to an electrode and generates current.>
And the OPV BHJ can often be assembled using simple techniques like roll-to-roll printing in ambient conditions.
However, in order for OPV devices to be a viable solution, they need to be more efficient.
The efficiency of an OPV device can be improved by changing the chemistry of the electron acceptor and donor compounds, the polymer properties, and tuning the processing conditions of the BHJ.
With so many parameters, quickly this becomes an intractable problem for experiments to solve.
This is where molecular simulation comes in. 
Molecular dynamics (MD), a simulation technique where atoms are represented by classical forces and their interactions are specified by attractive/repulsive potentials, can be used to probe the thermodynamic processes which determine how OPV compounds will self-assemble into a BHJ morphology.
Then we can use kinetic monte carlo (KMC) in concert with quantum chemical calculations (QCCs) to determine the charge mobility through these simulated morphologies.
By understanding how charge move through these systems, one can predict which OPVs will be most efficient.
However, this simulation workflow suffers from a problem of length scales:
Probing charge transport properties with QCCs requires the calculation of electron densities around each atom. 
But equilibrating this morphology at volumes which exceed the exciton dissociation length (~5-10 nm) is prohibitive if every individual atom is considered.
Coarse grain (CG) models, which group multiple atoms together into "super atoms" and using an effective potential to specify the forces acting upon the site, can be used to access length and time scales more relevant to the bulk polymer morphology.
After a bulk morphology is obtained, we can use backmapping, a process in which the atomistic detail can be reintegrated into a coarse grain model, can be used to restore atomistic detail for use in simulations like KMC/QCC.
This multiscale simulation workflow allows for OPV morphologiesto be equilibrated at length scales relevant to the bulk polymerand to regain the atomistic detail necessary later and from a better starting structure.
Currently software packages exist that do this but they require tedious manual input and are highly susceptible to user error.
PI Fothergill will design a simple, chemically sensible coarse-graining and backmapping package based on the SMILES chemical input language with a focus on OPVs.
This will allow for easier setup and execution of multiscale simulation, which can be part of the process to finding the next great OPV technology.

@@

A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
This can be useful for screening of potential OPV compounds.
<talk about VOTCA?>
<talk about TRUE simulations and reproducibility in the field>
<talk about our supercomputer allocations?>
<talk about what I've done already?>

@@

Helping to make research transferrable, reproducible, useable, and extensible. 
Wriitng tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
Training/teaching undergrads.
Working as part of a team.

### 2020-08-04 2pd.tex
writing for today. good progress on summary c:

\section*{Motivation}
<why do opvs matter>
<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Maziio2015}
Renewable energy is necessary.
Organic photovoltaics (OPVs) are a potential solution.
<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
Currently OPV devices are not efficient enough to solve this problem.
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
<opv performance is intimately linked with structure>
the interfacial area of the acceptor/donor regions \cite{mazzio} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
<how do we model this system?>

@@

\subsection*{Organic Photovoltaics}
<history>
<how opvs work>
The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can be used to generate excitons.
OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
Depending on the bulk morphology of these compounds, the exciton can travel to an accepto-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
<why morphology matters>
<segue into simulation>

>>>>

\section*{Motivation}
<why do opvs matter>
<energy demand is increasing and we need a nonpolluting cost-efficient way to provide electricity>
Global energy consumption 17 TW in 2010 to 27 TW in 2040 \cite{Mazzio2015}
Renewable energy is necessary.
Organic photovoltaics (OPVs) are a potential solution.
<image from nrel about solar cells efficiency>\cite{https://www.nrel.gov/pv/cell-efficiency.html}
OPVs are lightweight, low-cost, and flexible--in order to become the best solution they need better efficiency \cite{Mazzioi2015}.
Currently OPV devices are not efficient enough to solve this problem.
In order to make the most efficient opvs we need to find the best blend of compounds and the processing conditions that result in the best structure for those compounds.
<opv performance is intimately linked with structure>
the interfacial area of the acceptor/donor regions \cite{mazzio} the regioregularity of the polymer \cite{Kim2006} and electronic properties (HOMO level) of the compounds \cite{Scharber2006a}
With minor modifcations the number of compounds and the processing conditions can become infinite which makes this an intractable problem for experiment.
Functionalizing a molecule like ITIC can change how it packs in a crystal \cite{Swick2019a}.
By using a simulation pipeline, we can help to streamline the process of determining which opv materials will help to solve the energy crisis
Simulation also helps to give us insight into the atomic interaction which drive self assembly.
A complication of this simulation is that the features which are important to the performance of an opv span multiple length scales.
The electronic properties are important for light absorption, charge transfer \cite{Scharber2006,Hoppe2004,Mazzio2015}
while the bulk morphological properties are important: an exciton needs to be able to find an interface at which to dissociate before it decays through one of its non-radiative processes and one the charges are separated they need to reach an electrode in order to generate current and produce electricity.
<how do we model this system?>

<justification for what I'm doing>
the number of opv compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies\cite{dou2013}.
A P3HT:NFA blend was shown to have 11\% PCE, compared to the state-of-the-art 6.4\% in P3HT:PCBM. \cite{Baran2017}
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70-80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h) \cite{Baran2017}.
It is necessary to develop a simple easy to use pipeline to adapt to the constant changing chemistries of current OPV technologies. 
we need a flexible pipeline for coarse grain model generation for these new chemistries

@@

\subsection*{Organic Photovoltaics}
<history>
inorganic PV devices came first and are still most efficient, but they are more costly to produce, use rare elements, other environmental issue--they aren't the best solution for solar energy harvesting. 
first opv was tang1986<cite> used a bilyaer structure
Saricifti and Heeger 1992 <cite> discovered BHJ
BHJ with fullerene acceptor reported by Yu in 1995 -still state of the art morphology. <cite>
non fullerene acceptors, like ITIC, are helping to increase PCE \cite{S.Gurney2019}
A-D-A \cite{Yi2018} has some mention of the A-D-A moeity and why it is good <read further>
<how opvs work>
The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can be used to generate excitons.
OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk-heterojunction.
Depending on the bulk morphology of these compounds, the exciton can travel to an accepto-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.
<why morphology matters>
<segue into simulation>
